Unicode Implementation Issues \thanks { This is a working document for the Rexx Language Association (RexxLA). There will be one or more separate requirements documents. It is written in \LaTeX\ \fmtversion\ and was rendered \today\ using \enginedetails. }

### 2024-02-16 ARB/standards/work-in-progress/document/tex/standard/built-in_classes.tex
add cyrillic.rexx, rename unicode.md to Unicode_Requirements.md
upd

\hypertarget{built-in-classes}{%
\chapter{Built-in classes}\label{built-in-classes}}

\hypertarget{notation}{%
\section{Notation}\label{notation}}

@@

\hypertarget{object-class-and-method}{%
\section{Object, class and method}\label{object-class-and-method}}

@@

\hypertarget{the-object-class}{%
\subsection{The object class}\label{the-object-class}}

@@

\hypertarget{the-class-class}{%
\subsection{The class class}\label{the-class-class}}

@@

::method `' We can do all the operators by appeal to classic section 7.
::method'-' ::method `-'

@@

\hypertarget{the-supplier-class}{%
\section{The supplier class}\label{the-supplier-class}}

>>>>

%preprocessed texin
\chapter{Built-in classes}\label{built-in-classes}

\section{Notation}\label{notation}

@@

\section{Object, class and method}\label{object-class-and-method}

@@

\subsection{The object class}\label{the-object-class}

@@

\subsection{The class class}\label{the-class-class}

@@

::method `\textquotesingle{} We can do all the operators by appeal to
classic section 7. ::method'-' ::method `-'

@@

\section{The supplier class}\label{the-supplier-class}

### 2024-02-16 ARB/standards/work-in-progress/document/tex/standard/built-in_functions.tex
work in standard book production process including readme.md
upd

\hypertarget{built-in-functions}{%
\chapter{Built-in functions}\label{built-in-functions}}

\hypertarget{notation}{%
\section{Notation}\label{notation}}

@@

\hypertarget{routines-used-by-built-in-functions}{%
\section{Routines used by built-in
functions}\label{routines-used-by-built-in-functions}}

@@

\hypertarget{argument-checking}{%
\subsection{Argument checking}\label{argument-checking}}

@@

\hypertarget{raising-the-syntax-condition}{%
\subsection{Raising the SYNTAX
condition}\label{raising-the-syntax-condition}}

@@

\hypertarget{character-built-in-functions}{%
\section{Character built-in
functions}\label{character-built-in-functions}}

@@

\hypertarget{abbrev}{%
\subsection{ABBREV}\label{abbrev}}

@@

\hypertarget{center}{%
\subsection{CENTER}\label{center}}

@@

\hypertarget{centre}{%
\subsection{CENTRE}\label{centre}}

@@

\hypertarget{changestr}{%
\subsection{CHANGESTR}\label{changestr}}

@@

\hypertarget{compare}{%
\subsection{COMPARE}\label{compare}}

@@

\hypertarget{copies}{%
\subsection{COPIES}\label{copies}}

@@

\hypertarget{countstr}{%
\subsection{COUNTSTR}\label{countstr}}

@@

\hypertarget{datatype}{%
\subsection{DATATYPE}\label{datatype}}

@@

\hypertarget{delstr}{%
\subsection{DELSTR}\label{delstr}}

@@

\hypertarget{delword}{%
\subsection{DELWORD}\label{delword}}

@@

\hypertarget{insert}{%
\subsection{INSERT}\label{insert}}

@@

\hypertarget{lastpos}{%
\subsection{LASTPOS}\label{lastpos}}

@@

\hypertarget{left}{%
\subsection{LEFT}\label{left}}

@@

\hypertarget{overlay}{%
\subsection{OVERLAY}\label{overlay}}

@@

\hypertarget{reverse}{%
\subsection{REVERSE}\label{reverse}}

@@

\hypertarget{right}{%
\subsection{RIGHT}\label{right}}

@@

\hypertarget{space}{%
\subsection{SPACE}\label{space}}

@@

\hypertarget{strip}{%
\subsection{STRIP}\label{strip}}

@@

\hypertarget{substr}{%
\subsection{SUBSTR}\label{substr}}

@@

\hypertarget{subword}{%
\subsection{SUBWORD}\label{subword}}

@@

\hypertarget{translate}{%
\subsection{TRANSLATE}\label{translate}}

@@

\hypertarget{verify}{%
\subsection{VERIFY}\label{verify}}

@@

\hypertarget{word}{%
\subsection{WORD}\label{word}}

@@

\hypertarget{wordindex}{%
\subsection{WORDINDEX}\label{wordindex}}

@@

\hypertarget{wordlength}{%
\subsection{WORDLENGTH}\label{wordlength}}

@@

\hypertarget{wordpos}{%
\subsection{WORDPOS}\label{wordpos}}

@@

\hypertarget{words}{%
\subsection{WORDS}\label{words}}

@@

\hypertarget{xrange}{%
\subsection{XRANGE}\label{xrange}}

@@

\hypertarget{arithmetic-built-in-functions}{%
\section{Arithmetic built-in
functions}\label{arithmetic-built-in-functions}}

@@

\hypertarget{abs}{%
\subsection{ABS}\label{abs}}

@@

\hypertarget{format}{%
\subsection{FORMAT}\label{format}}

@@

\hypertarget{max}{%
\subsection{MAX}\label{max}}

@@

\hypertarget{min}{%
\subsection{MIN}\label{min}}

@@

\hypertarget{sign}{%
\subsection{SIGN}\label{sign}}

@@

\hypertarget{trunc}{%
\subsection{TRUNC}\label{trunc}}

@@

\hypertarget{state-built-in-functions}{%
\section{State built-in functions}\label{state-built-in-functions}}

@@

\hypertarget{address}{%
\subsection{ADDRESS}\label{address}}

@@

\hypertarget{arg}{%
\subsection{ARG}\label{arg}}

@@

\hypertarget{condition}{%
\subsection{CONDITION}\label{condition}}

@@

\hypertarget{errortext}{%
\subsection{ERRORTEXT}\label{errortext}}

@@

\hypertarget{form}{%
\subsection{FORM}\label{form}}

@@

\hypertarget{fuzz}{%
\subsection{FUZZ}\label{fuzz}}

@@

\hypertarget{sourceline}{%
\subsection{SOURCELINE}\label{sourceline}}

@@

\hypertarget{trace}{%
\subsection{TRACE}\label{trace}}

@@

\hypertarget{b2xx}{%
\subsection{B2xX}\label{b2xx}}

@@

\hypertarget{bitand}{%
\subsection{BITAND}\label{bitand}}

@@

\hypertarget{bitor}{%
\subsection{BITOR}\label{bitor}}

@@

\hypertarget{bitxor}{%
\subsection{BITXOR}\label{bitxor}}

@@

\hypertarget{c2d}{%
\subsection{C2D}\label{c2d}}

@@

\hypertarget{d2c}{%
\subsection{D2C}\label{d2c}}

@@

\hypertarget{d2x}{%
\subsection{D2X}\label{d2x}}

@@

\hypertarget{x2b}{%
\subsection{X2B}\label{x2b}}

@@

\hypertarget{x2c}{%
\subsection{X2C}\label{x2c}}

@@

\hypertarget{x2d}{%
\subsection{X2D}\label{x2d}}

@@

\hypertarget{inputoutput-built-in-functions}{%
\section{Input/Output built-in
functions}\label{inputoutput-built-in-functions}}

@@

\hypertarget{charout}{%
\subsection{CHAROUT}\label{charout}}

@@

\hypertarget{chars}{%
\subsection{CHARS}\label{chars}}

@@

\hypertarget{linein}{%
\subsection{LINEIN}\label{linein}}

@@

\hypertarget{lineout}{%
\subsection{LINEOUT}\label{lineout}}

@@

\hypertarget{qualify}{%
\subsection{QUALIFY}\label{qualify}}

@@

\hypertarget{stream}{%
\subsection{STREAM}\label{stream}}

@@

\hypertarget{other-built-in-functions}{%
\section{Other built-in functions}\label{other-built-in-functions}}

\hypertarget{date}{%
\subsection{DATE}\label{date}}

@@

\hypertarget{queued}{%
\subsection{QUEUED}\label{queued}}

@@

\hypertarget{random}{%
\subsection{RANDOM}\label{random}}

@@

\hypertarget{symbol}{%
\subsection{SYMBOL}\label{symbol}}

@@

\hypertarget{time}{%
\subsection{TIME}\label{time}}

@@

\hypertarget{queued-1}{%
\subsection{QUEUED}\label{queued-1}}

@@

\hypertarget{random-1}{%
\subsection{RANDOM}\label{random-1}}

@@

\hypertarget{symbol-1}{%
\subsection{SYMBOL}\label{symbol-1}}

@@

\hypertarget{time-1}{%
\subsection{TIME}\label{time-1}}

>>>>

%preprocessed texin
\chapter{Built-in functions}\label{built-in-functions}

\section{Notation}\label{notation}

@@

\section{Routines used by built-in
functions}\label{routines-used-by-built-in-functions}

@@

\subsection{Argument checking}\label{argument-checking}

@@

\subsection{Raising the SYNTAX
condition}\label{raising-the-syntax-condition}

@@

\section{Character built-in
functions}\label{character-built-in-functions}

@@

\subsection{ABBREV}\label{abbrev}

@@

\subsection{CENTER}\label{center}

@@

\subsection{CENTRE}\label{centre}

@@

\subsection{CHANGESTR}\label{changestr}

@@

\subsection{COMPARE}\label{compare}

@@

\subsection{COPIES}\label{copies}

@@

\subsection{COUNTSTR}\label{countstr}

@@

\subsection{DATATYPE}\label{datatype}

@@

\subsection{DELSTR}\label{delstr}

@@

\subsection{DELWORD}\label{delword}

@@

\subsection{INSERT}\label{insert}

@@

\subsection{LASTPOS}\label{lastpos}

@@

\subsection{LEFT}\label{left}

@@

\subsection{OVERLAY}\label{overlay}

@@

\subsection{REVERSE}\label{reverse}

@@

\subsection{RIGHT}\label{right}

@@

\subsection{SPACE}\label{space}

@@

\subsection{STRIP}\label{strip}

@@

\subsection{SUBSTR}\label{substr}

@@

\subsection{SUBWORD}\label{subword}

@@

\subsection{TRANSLATE}\label{translate}

@@

\subsection{VERIFY}\label{verify}

@@

\subsection{WORD}\label{word}

@@

\subsection{WORDINDEX}\label{wordindex}

@@

\subsection{WORDLENGTH}\label{wordlength}

@@

\subsection{WORDPOS}\label{wordpos}

@@

\subsection{WORDS}\label{words}

@@

\subsection{XRANGE}\label{xrange}

@@

\section{Arithmetic built-in
functions}\label{arithmetic-built-in-functions}

@@

\subsection{ABS}\label{abs}

@@

\subsection{FORMAT}\label{format}

@@

\subsection{MAX}\label{max}

@@

\subsection{MIN}\label{min}

@@

\subsection{SIGN}\label{sign}

@@

\subsection{TRUNC}\label{trunc}

@@

\section{State built-in functions}\label{state-built-in-functions}

@@

\subsection{ADDRESS}\label{address}

@@

\subsection{ARG}\label{arg}

@@

\subsection{CONDITION}\label{condition}

@@

\subsection{ERRORTEXT}\label{errortext}

@@

\subsection{FORM}\label{form}

@@

\subsection{FUZZ}\label{fuzz}

@@

\subsection{SOURCELINE}\label{sourceline}

@@

\subsection{TRACE}\label{trace}

@@

\subsection{B2xX}\label{b2xx}

@@

\subsection{BITAND}\label{bitand}

@@

\subsection{BITOR}\label{bitor}

@@

\subsection{BITXOR}\label{bitxor}

@@

\subsection{C2D}\label{c2d}

@@

\subsection{D2C}\label{d2c}

@@

\subsection{D2X}\label{d2x}

@@

\subsection{X2B}\label{x2b}

@@

\subsection{X2C}\label{x2c}

@@

\subsection{X2D}\label{x2d}

@@

\section{Input/Output built-in
functions}\label{inputoutput-built-in-functions}

@@

\subsection{CHAROUT}\label{charout}

@@

\subsection{CHARS}\label{chars}

@@

\subsection{LINEIN}\label{linein}

@@

\subsection{LINEOUT}\label{lineout}

@@

\subsection{QUALIFY}\label{qualify}

@@

\subsection{STREAM}\label{stream}

@@

\section{Other built-in functions}\label{other-built-in-functions}

\subsection{DATE}\label{date}

@@

\subsection{QUEUED}\label{queued}

@@

\subsection{RANDOM}\label{random}

@@

\subsection{SYMBOL}\label{symbol}

@@

\subsection{TIME}\label{time}

@@

\subsection{QUEUED}\label{queued-1}

@@

\subsection{RANDOM}\label{random-1}

@@

\subsection{SYMBOL}\label{symbol-1}

@@

\subsection{TIME}\label{time-1}

### 2024-02-16 ARB/standards/work-in-progress/document/tex/standard/configuration.tex
work in standard book production process including readme.md
upd

\hypertarget{configuration}{%
\chapter{Configuration}\label{configuration}}

@@

\hypertarget{notation}{%
\section{Notation}\label{notation}}

@@

\hypertarget{notation-for-completion-response-and-conditions}{%
\subsection{Notation for completion response and
conditions}\label{notation-for-completion-response-and-conditions}}

@@

\hypertarget{processing-initiation}{%
\section{Processing initiation}\label{processing-initiation}}

@@

\hypertarget{api-start}{%
\subsection{API Start}\label{api-start}}

@@

\hypertarget{source-programs-and-character-sets}{%
\section{Source programs and character
sets}\label{source-programs-and-character-sets}}

@@

\hypertarget{syntactic_characters}{%
\subsection{Syntactic\_characters}\label{syntactic_characters}}

@@

\hypertarget{extra_letters}{%
\subsection{Extra\_letters}\label{extra_letters}}

@@

\hypertarget{other_blank_characters}{%
\subsection{Other\_blank\_characters}\label{other_blank_characters}}

@@

\hypertarget{other_negators}{%
\subsection{Other\_negators}\label{other_negators}}

@@

\begin{itemize}
\item
  \begin{itemize}
  \tightlist
  \item
    circumflex accent, caret;
  \end{itemize}
\item
  --- not sign.
\end{itemize}

\hypertarget{other_characters}{%
\subsection{Other\_characters}\label{other_characters}}

@@

\hypertarget{configuration-characters-and-encoding}{%
\section{Configuration characters and
encoding}\label{configuration-characters-and-encoding}}

@@

\hypertarget{config_sourcechar}{%
\subsection{Config\_SourceChar}\label{config_sourcechar}}

@@

\hypertarget{config_otherblankcharacters}{%
\subsection{Config\_OtherBlankCharacters}\label{config_otherblankcharacters}}

@@

\hypertarget{config_upper}{%
\subsection{Config\_Upper}\label{config_upper}}

@@

\hypertarget{config_lower}{%
\subsection{Config\_Lower}\label{config_lower}}

@@

\hypertarget{config_compare}{%
\subsection{Config\_Compare}\label{config_compare}}

@@

\hypertarget{config-_b2c}{%
\subsection{Config \_B2C}\label{config-_b2c}}

@@

\hypertarget{config_c2b}{%
\subsection{Config\_C2B}\label{config_c2b}}

@@

\hypertarget{config_substr}{%
\subsection{Config\_Substr}\label{config_substr}}

@@

\hypertarget{config-length}{%
\subsection{Config Length}\label{config-length}}

@@

\hypertarget{config_xrange}{%
\subsection{Config\_Xrange}\label{config_xrange}}

@@

\hypertarget{objects}{%
\section{Objects}\label{objects}}

@@

\hypertarget{config_objectnew}{%
\subsection{Config\_ObjectNew}\label{config_objectnew}}

@@

\hypertarget{config_array_size}{%
\subsection{Config\_Array\_Size}\label{config_array_size}}

@@

\hypertarget{config_array_put}{%
\subsection{Config\_Array\_Put}\label{config_array_put}}

@@

\hypertarget{config_array_at}{%
\subsection{Config\_Array\_At}\label{config_array_at}}

@@

\hypertarget{config_array_hasindex}{%
\subsection{Config\_Array\_Hasindex}\label{config_array_hasindex}}

@@

\hypertarget{config_array_remove}{%
\subsection{Config\_Array\_Remove}\label{config_array_remove}}

@@

\hypertarget{commands}{%
\section{Commands}\label{commands}}

@@

\hypertarget{config-_command}{%
\subsection{Config \_Command}\label{config-_command}}

@@

\hypertarget{external-routines}{%
\section{External routines}\label{external-routines}}

@@

\hypertarget{config_externalroutine}{%
\subsection{Config\_ExternalRoutine}\label{config_externalroutine}}

@@

\hypertarget{config_externalmethod}{%
\subsection{Config\_ExternalMethod}\label{config_externalmethod}}

@@

\hypertarget{config-push}{%
\subsection{Config Push}\label{config-push}}

@@

\hypertarget{contig_queue}{%
\subsection{Contig\_Queue}\label{contig_queue}}

@@

\hypertarget{config_pull}{%
\subsection{Config\_Pull}\label{config_pull}}

@@

\hypertarget{contig_queued}{%
\subsection{Contig\_Queued}\label{contig_queued}}

@@

\hypertarget{streams}{%
\section{Streams}\label{streams}}

@@

\hypertarget{config-_stream_charin}{%
\subsection{Config \_Stream\_Charin}\label{config-_stream_charin}}

@@

\hypertarget{config_stream_position}{%
\subsection{Config\_Stream\_Position}\label{config_stream_position}}

@@

\hypertarget{config-_stream_command}{%
\subsection{Config \_Stream\_Command}\label{config-_stream_command}}

@@

\hypertarget{config_stream_state}{%
\subsection{Config\_Stream\_State}\label{config_stream_state}}

@@

\hypertarget{config_stream_charout}{%
\subsection{Config\_Stream\_Charout}\label{config_stream_charout}}

@@

\hypertarget{config_stream_qualified}{%
\subsection{Config\_Stream\_Qualified}\label{config_stream_qualified}}

@@

\hypertarget{config_stream_unique}{%
\subsection{Config\_Stream\_Unique}\label{config_stream_unique}}

@@

\hypertarget{config_stream_query}{%
\subsection{Config\_Stream\_Query}\label{config_stream_query}}

@@

\hypertarget{config_stream_close}{%
\subsection{Config\_Stream\_Close}\label{config_stream_close}}

@@

\hypertarget{config-_stream_count}{%
\subsection{Config \_Stream\_Count}\label{config-_stream_count}}

@@

\hypertarget{external-variable-pools}{%
\section{External variable pools}\label{external-variable-pools}}

@@

\hypertarget{config-get}{%
\subsection{Config Get}\label{config-get}}

@@

\hypertarget{config-set}{%
\subsection{Config Set}\label{config-set}}

@@

\hypertarget{configuration-characteristics}{%
\section{Configuration
characteristics}\label{configuration-characteristics}}

@@

\hypertarget{config_constants}{%
\subsection{Config\_Constants}\label{config_constants}}

@@

\hypertarget{configuration-routines}{%
\section{Configuration routines}\label{configuration-routines}}

@@

\hypertarget{config_trace_query}{%
\subsection{Config\_Trace\_Query}\label{config_trace_query}}

@@

\hypertarget{config_trace_input}{%
\subsection{Config\_Trace\_Input}\label{config_trace_input}}

@@

\hypertarget{config_trace_output}{%
\subsection{Config\_Trace\_Output}\label{config_trace_output}}

@@

\hypertarget{config-_default_input}{%
\subsection{Config \_Default\_Input}\label{config-_default_input}}

@@

\hypertarget{config_default_output}{%
\subsection{Config\_Default\_Output}\label{config_default_output}}

@@

\hypertarget{config_initialization}{%
\subsection{Config\_Initialization}\label{config_initialization}}

@@

\hypertarget{config_termination}{%
\subsection{Config\_Termination}\label{config_termination}}

@@

\hypertarget{config_halt_query}{%
\subsection{Config\_Halt\_Query}\label{config_halt_query}}

@@

\hypertarget{config-_nosource}{%
\subsection{Config \_NoSource}\label{config-_nosource}}

@@

\hypertarget{config_time}{%
\subsection{Config\_Time}\label{config_time}}

@@

\hypertarget{config_random_seed}{%
\subsection{Config\_Random\_Seed}\label{config_random_seed}}

@@

\hypertarget{config_random_next}{%
\subsection{Config\_Random\_Next}\label{config_random_next}}

@@

\hypertarget{config_options}{%
\subsection{Config\_Options}\label{config_options}}

@@

\hypertarget{traps}{%
\section{Traps}\label{traps}}

@@

\hypertarget{variable-pool}{%
\section{Variable pool}\label{variable-pool}}

@@

\hypertarget{api-set}{%
\subsection{API Set}\label{api-set}}

@@

\hypertarget{api-value}{%
\subsection{API Value}\label{api-value}}

@@

\hypertarget{api_drop}{%
\subsection{API\_Drop}\label{api_drop}}

@@

\hypertarget{api-setdirect}{%
\subsection{API SetDirect}\label{api-setdirect}}

@@

\hypertarget{api_valuedirect}{%
\subsection{API\_ValueDirect}\label{api_valuedirect}}

@@

\hypertarget{api-dropdirect}{%
\subsection{API DropDirect}\label{api-dropdirect}}

@@

\hypertarget{api-valueother}{%
\subsection{API ValueOther}\label{api-valueother}}

@@

\hypertarget{api-next}{%
\subsection{API Next}\label{api-next}}

@@

\hypertarget{api-nextvariable}{%
\subsection{API NextVariable}\label{api-nextvariable}}

>>>>

%preprocessed texin
\chapter{Configuration}\label{configuration}

@@

\section{Notation}\label{notation}

@@

\subsection{Notation for completion response and
conditions}\label{notation-for-completion-response-and-conditions}

@@

\section{Processing initiation}\label{processing-initiation}

@@

\subsection{API Start}\label{api-start}

@@

\section{Source programs and character
sets}\label{source-programs-and-character-sets}

@@

\subsection{Syntactic\_characters}\label{syntactic_characters}

@@

\subsection{Extra\_letters}\label{extra_letters}

@@

\subsection{Other\_blank\_characters}\label{other_blank_characters}

@@

\subsection{Other\_negators}\label{other_negators}

@@

\begin{itemize}
\tightlist
\item
  \begin{itemize}
  \tightlist
  \item
    circumflex accent, caret;
  \end{itemize}
\item
  --- not sign.
\end{itemize}

\subsection{Other\_characters}\label{other_characters}

@@

\section{Configuration characters and
encoding}\label{configuration-characters-and-encoding}

@@

\subsection{Config\_SourceChar}\label{config_sourcechar}

@@

\subsection{Config\_OtherBlankCharacters}\label{config_otherblankcharacters}

@@

\subsection{Config\_Upper}\label{config_upper}

@@

\subsection{Config\_Lower}\label{config_lower}

@@

\subsection{Config\_Compare}\label{config_compare}

@@

\subsection{Config \_B2C}\label{config-_b2c}

@@

\subsection{Config\_C2B}\label{config_c2b}

@@

\subsection{Config\_Substr}\label{config_substr}

@@

\subsection{Config Length}\label{config-length}

@@

\subsection{Config\_Xrange}\label{config_xrange}

@@

\section{Objects}\label{objects}

@@

\subsection{Config\_ObjectNew}\label{config_objectnew}

@@

\subsection{Config\_Array\_Size}\label{config_array_size}

@@

\subsection{Config\_Array\_Put}\label{config_array_put}

@@

\subsection{Config\_Array\_At}\label{config_array_at}

@@

\subsection{Config\_Array\_Hasindex}\label{config_array_hasindex}

@@

\subsection{Config\_Array\_Remove}\label{config_array_remove}

@@

\section{Commands}\label{commands}

@@

\subsection{Config \_Command}\label{config-_command}

@@

\section{External routines}\label{external-routines}

@@

\subsection{Config\_ExternalRoutine}\label{config_externalroutine}

@@

\subsection{Config\_ExternalMethod}\label{config_externalmethod}

@@

\subsection{Config Push}\label{config-push}

@@

\subsection{Contig\_Queue}\label{contig_queue}

@@

\subsection{Config\_Pull}\label{config_pull}

@@

\subsection{Contig\_Queued}\label{contig_queued}

@@

\section{Streams}\label{streams}

@@

\subsection{Config \_Stream\_Charin}\label{config-_stream_charin}

@@

\subsection{Config\_Stream\_Position}\label{config_stream_position}

@@

\subsection{Config \_Stream\_Command}\label{config-_stream_command}

@@

\subsection{Config\_Stream\_State}\label{config_stream_state}

@@

\subsection{Config\_Stream\_Charout}\label{config_stream_charout}

@@

\subsection{Config\_Stream\_Qualified}\label{config_stream_qualified}

@@

\subsection{Config\_Stream\_Unique}\label{config_stream_unique}

@@

\subsection{Config\_Stream\_Query}\label{config_stream_query}

@@

\subsection{Config\_Stream\_Close}\label{config_stream_close}

@@

\subsection{Config \_Stream\_Count}\label{config-_stream_count}

@@

\section{External variable pools}\label{external-variable-pools}

@@

\subsection{Config Get}\label{config-get}

@@

\subsection{Config Set}\label{config-set}

@@

\section{Configuration
characteristics}\label{configuration-characteristics}

@@

\subsection{Config\_Constants}\label{config_constants}

@@

\section{Configuration routines}\label{configuration-routines}

@@

\subsection{Config\_Trace\_Query}\label{config_trace_query}

@@

\subsection{Config\_Trace\_Input}\label{config_trace_input}

@@

\subsection{Config\_Trace\_Output}\label{config_trace_output}

@@

\subsection{Config \_Default\_Input}\label{config-_default_input}

@@

\subsection{Config\_Default\_Output}\label{config_default_output}

@@

\subsection{Config\_Initialization}\label{config_initialization}

@@

\subsection{Config\_Termination}\label{config_termination}

@@

\subsection{Config\_Halt\_Query}\label{config_halt_query}

@@

\subsection{Config \_NoSource}\label{config-_nosource}

@@

\subsection{Config\_Time}\label{config_time}

@@

\subsection{Config\_Random\_Seed}\label{config_random_seed}

@@

\subsection{Config\_Random\_Next}\label{config_random_next}

@@

\subsection{Config\_Options}\label{config_options}

@@

\section{Traps}\label{traps}

@@

\section{Variable pool}\label{variable-pool}

@@

\subsection{API Set}\label{api-set}

@@

\subsection{API Value}\label{api-value}

@@

\subsection{API\_Drop}\label{api_drop}

@@

\subsection{API SetDirect}\label{api-setdirect}

@@

\subsection{API\_ValueDirect}\label{api_valuedirect}

@@

\subsection{API DropDirect}\label{api-dropdirect}

@@

\subsection{API ValueOther}\label{api-valueother}

@@

\subsection{API Next}\label{api-next}

@@

\subsection{API NextVariable}\label{api-nextvariable}
